---
title: "NetworkSim"
output:
  md_document: 
     variant: markdown_github
---

# NetworkSim

__*Current version*__:1.1.1, __*Depends*__: R (>= 3.4.0)

## Description

NetworkSim, an R package that provides two different ways for undirected network comparison, which contains the structural equivalence based on paired nodes and the graphlet-based systematic measurement. 

## Installation
NetworkSim currently needs to be installed using devtools. The igraph and orca packages also need to be installed.

```{r eval=F}
devtools::install_github("QiliShi/NetworkSim")
```

## Running times 
Create different sizes of PPI networks
```{r}
library(NetworkSim)
library(igraph)
small_net1 <-subnet(databases.net,nodes = c(names(neighbors(databases.net,'TP53')),'TP53')[1:75],neighbors = F)
small_net2 <-subnet(databases.net,nodes = c(names(neighbors(databases.net,'TP53')),'TP53')[40:120],neighbors = F)

middle_net1 <-subnet(databases.net,nodes = c(names(neighbors(databases.net,'TP53')),'TP53')[1:300],neighbors = F)
middle_net2 <-subnet(databases.net,nodes = c(names(neighbors(databases.net,'TP53')),'TP53')[150:450],neighbors = F)

nodes <- c(names(neighbors(databases.net,'TP53')),'TP53',names(neighbors(databases.net,'MYC')),'MYC',
           names(neighbors(databases.net,'APP')))
large_net1 <-subnet(databases.net,nodes = nodes[1:2000],neighbors = F)
large_net2 <-subnet(databases.net,nodes = nodes[500:3300],neighbors = F)

nodes <- names(V(databases.net))
Vlarge_net1 <-subnet(databases.net,nodes = sample(nodes,15000),neighbors = F)
Vlarge_net2 <-subnet(databases.net,nodes = sample(nodes,15000),neighbors = F)
```
Measure the running times on small (tens of nodes, hundreds of edges), medium (hundreds of nodes, thousands of edges), large ( thousands of nodes, tens of thousands of edges), and very large ( tens of thousands of nodes, hundreds of thousands of edges) sizes of PPI networks from Human Protein Reference Database (HPRD), BioGRID and mentha databases.
```{r}
system.time(paired <- nodesCom(middle_net1,middle_net2))

system.time(netSE(middle_net1,middle_net2,paired[1,1],paired[1,2]))

system.time(netODA(middle_net1,middle_net2))
```
## Examples

Create the input networks with igraph types

1.Create networks from our intergrated human PPI network.

```{r}
TCGA_AF_2687.net<-subnet(net=databases.net, nodes=TCGA_AF_2687.Muts)
```
2.Create networks from user's own data, which should be a data frame containing a symbolic edge list in the two columns.
For example:
```{r}
library(sand)
g <- graph.data.frame(elist.lazega,directed=F)
```

Get the paired nodes between two networks
```{r}
paired<-nodesCom(TCGA_AF_2687.net, TCGA_A6_2686.net)
```

Calculate a similarity of a pair of nodes
```{r}
netSE(TCGA_AF_2687.net, TCGA_A6_2686.net, 'NMT1', 'MED10')
```

Calculate all structural equivalence of the paired nodes
```{r}
paired.SE<-netSEs(TCGA_AF_2687.net,TCGA_A6_2686.net, paired)
```

The overall agreement based on graphlets of two networks can be gained by
```{r}
netODA(TCGA_AF_2687.net, TCGA_A6_2686.net)
```
